\documentclass[11pt,a4paper]{moderncv}

% Styl i kolory CV
\moderncvstyle{classic}
\moderncvcolor{blue}

% Pakiety
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

% Footer settings
\rfoot{Your footer here}

\renewcommand{\footrulewidth}{0.4pt} % Thickness of the line separating the footer from the rest of the page

% Dane osobowe
\name{Piotr}{Próchnicki}
\title{CV – IT support}
\email{piotr.prochnicki@gmail.com}
\homepage{piotrit2015.github.io}
\social[linkedin]{piotr-prochnicki}

\begin{document}

\makecvtitle

% Podsumowanie zawodowe
\section*{Professional Summary}
Dedicated IT support specialist with a background in computer science and years of experience in administrative and technical environments. Responsible, communicative and experienced in supporting users, installing systems and resolving IT issues.

% Umiejętności
\section{Skills}
\cvitem{Systems}{Windows, Linux, basic knowledge of computer networks}
\cvitem{Tools}{Docker, LAMP stack, basic PHP, MS Office, email systems}
\cvitem{Support}{Remote IT support, hardware/software configuration, end-user assistance}
\cvitem{Soft Skills}{Responsibility, punctuality, teamwork, process documentation}

% Wykształcenie
\section{Work Experience}

\cventry{05.2023 -- 09.2023}{DevOps Engineer Intern}{HXS Sp. z o.o. Sp.k.}{}{}{
  \begin{itemize}
    \item Installed LAMP stack and configured Docker containers.
    \item Acquired basic PHP programming skills.
  \end{itemize}
}

\cventry{12.2022 -- 03.2023}{Administrative Assistant Intern}{Tax Unit Sp. z o.o.}{}{}{
  \begin{itemize}
    \item Archived documents and handled official correspondence.
  \end{itemize}
}

\cventry{03.2022 -- 04.2022}{Online Store Assistant Intern}{Charity Polska}{}{}{
  \begin{itemize}
    \item Maintained online store: product listing and packaging.
  \end{itemize}
}

\cventry{09.2020 -- 12.2020}{Office Assistant Intern}{Grupa Center}{}{}{
  \begin{itemize}
    \item Operated store management software and created product descriptions.
  \end{itemize}
}

\cventry{11.2018 -- 06.2020}{Administrative Office Worker}{HR Team Sp. z o.o.}{}{}{
  \begin{itemize}
    \item Handled data, emails, and office documentation.
  \end{itemize}
}

\cventry{07.2017 -- 09.2017}{Cisco Services Engineer Intern}{Cisco Systems}{}{}{
  \begin{itemize}
    \item Worked in an international team; used Python and supported computer networks.
  \end{itemize}
}

\cventry{03.2017 -- 04.2017}{IT Technician}{COGITO Association}{}{}{
  \begin{itemize}
    \item Maintained IT infrastructure and local network systems.
  \end{itemize}
}

\cventry{10.2016 -- 12.2016}{Office Technician}{Kraków City Hall}{}{}{
  \begin{itemize}
    \item Provided IT support within the municipal office.
  \end{itemize}
}

\cventry{07.2015 -- 09.2015}{Office Technician}{Lesser Poland Voivodeship Office}{}{}{
  \begin{itemize}
    \item Provided IT support within the government office.
  \end{itemize}
}


% Języki
\section{Languages}
\cvitem{Polish}{Native}
\cvitem{English}{B2}
\cvitem{French}{A2}

\fancyfoot[LE,RO]{I agree to the processing of personal data provided in this document for realising the recruitment process pursuant to the Personal Data Protection Act of 10 May 2018 (Journal of Laws 2018, item 1000) and in agreement with Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 April 2016 on the protection of natural persons with regard to the processing of personal data and on the free movement of such data, and repealing Directive 95/46/EC (General Data Protection Regulation).}

\newpage

\section{Education}

\cventry{2015 -- 2017}{AGH University of Science and Technology, Kraków}{Applied Computer Science}{Industrial IT Systems}{MSc Eng.}{
  \begin{itemize}
    \item Master's thesis: "Principal Component Analysis of RXES Spectra" (Python).
  \end{itemize}
}

\cventry{2008 -- 2015}{AGH University of Science and Technology, Kraków}{Medical Physics}{}{BSc Eng.}{
  \begin{itemize}
    \item Bachelor's thesis: "Graphene and Carbon Nanotubes: Their Applications and Physicochemical Properties".
  \end{itemize}
}


\end{document}




